% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
% (c) 2009 Derek R. Hildreth <derek@derekhildreth.com> http://www.derekhildreth.com 
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

% GENERAL NOTE:  There may be some notes specific to myself. If you're only interested in my LaTeX source or it doesn't make sense, please disregard it.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[pdftex]{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=black,%
    filecolor=black,%
    linkcolor=black,%
    urlcolor=black     % can put red here to visualize the links
}
\urlstyle{same}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

\definecolor{darkGrey}{gray}{.35}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
%\newcommand{\resheading}[1]{{\large \colorbox{Cyan}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\resheading}[1]{{\large \textbf{#1}}}
%\newcommand{\resheading}[1]{{\large \colorbox{darkGrey}{\color{white}\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}
% Personal Info
%\newcommand{\email}{\href{mailto:pmsolfest@gmail.com}{pmsolfest@gmail.com}}
%\newcommand{\address}{{\footnotesize 20 S. 41st St, Apt. 58, Council Bluffs, IA 51501}}
%\newcommand{\phone}{(651) 325-8903}
% NG Info
\newcommand{\email}{\href{mailto:peter.solfest@ngc.com}{peter.solfest@ngc.com}}
\newcommand{\address}{{\footnotesize Northrop Grumman Corporation, 3200 Samson Way, Bellevue, NE 68123}}
\newcommand{\phone}{(651) 325-8903}

%-----------------------------------------------------------

%-----------------------------------------------------------
%General Resume Tips
%   No periods!  Technically, nothing in this document is a full sentence.
%   Use parallelism by ending key words with the same thing,  i.e. "Coordinated; Designed; Communicated".
%   More tips on bottom of this LaTeX document.
%-----------------------------------------------------------

\begin{document}

\newcommand{\mywebheader}{
\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}
  \textbf{\LARGE Peter Solfest} & \email \\
    \address & \phone  %\\
  %& Clearance Level: Secret
\end{tabular*}
\\
\vspace{0.1in}}

% CHANGE HEADER SOURCE HERE
\mywebheader

%%-------------SUMMARY-----------------%
\resheading{Summary}

  I develop and engineer software solutions and models using state-of-the-art techniques and technologies.
  I am especially interested in positions that leverage my applied/computational mathematics and physics
   background to solve problems for customers in the space domain.

  \vspace{0.1in}

%---------BEGIN WORK EXPERIENCE--------%
\resheading{Professional Experience}
\begin{itemize}
\item%NG work    
  \ressubheading{Mathematician}{\href{https://www.northropgrumman.com}{Northrop Grumman}}{
      \href{http://www.northropgrumman.com/Capabilities/SpaceWeatherAnalysis/Pages/default.aspx}{SWAFS},
        Weather and Space Impacts Research and Development Center}{Feb 2017 -- present}
  {\footnotesize
  \begin{itemize}  
    %\resitem{Primary Responsibilities: modernize software infrastructure, develop/improve software
      %    processes, develop innovative  new applications to demonstrate space weather impacts,
      %    mathematical validation of algorithms}
    \resitem{Roles: SWAFS Tech Lead, Research Assistant, SWAFS Software Developer}
  \end{itemize}
  }
\item%ARL work    
  \ressubheading{Engineering Scientist Associate}{\href{https://www.arlut.utexas.edu}{Applied Research Laboratories, UT}}{Space and Geophysics Laboratory}{Oct 2015 -- Jan 2017}
  {\footnotesize
 % \begin{itemize}  
  %  \resitem{Major Projects: data assimilating ionospheric models, web services for supplying models}
  %\end{itemize}
  }
\item
  \ressubheading{Research Assistant}{\href{https://www.cs.umn.edu}{University of Minnesota}}{Dept. of Computer Science}{July 2014 -- Mar 2015}
\item%calculus instructor
  \ressubheading{Calculus Instructor}{\href{www.mtu.edu/math/}{Michigan Tech Dept. of Mathematics}}{Calculus 1 and 2}{Jan 2013 -- June 2014 (4 semesters)}
\item%LPSA
	\ressubheading{Lunar and Planetary Space Academy}{NASA - Goddard, MD}{Instrumentation development for space based Gamma Ray Spectroscopy}{Summer 2011}

\begin{comment}
\item%physics TA
  \ressubheading{Lab TA}{\href{www.mtu.edu/physics}{Michigan Tech}}{Introductory Mechanics, Electronics, Mathematica}{Aug 2009 -- Apr 2012}
	{\footnotesize
	\begin{itemize}
		\resitem{Responsibilities: grade labs; lead lab sections; assist students with Mathematica}
		\resitem{Mathlab (Aug 2009 - Apr 2011), Mechanics (Aug 2010 - Dec 2011), Electronics (Jan 2012 - May 2012)}
%		\resitem{Both semesters mid-term student evaluations rated me above 4.6 out of 5 as an instructor}
	\end{itemize}
	}
\item%mathlab LC
  \ressubheading{MathLab Lab Consultant}{\href{www.mtu.edu/math/}{Michigan Tech Dept. of Mathematical Sciences}}{Calculus 1,2, and 3}{Jan 2009 -- Apr 2011}
	{\footnotesize
	\begin{itemize}
%		\resitem{At Michigan Tech Mathlab supplements calculus classes by having the students perform mathematics similar to their class using Mathematica}
	%	\resitem{Responsibilities: Help students with the labs in Mathematica; Help students with related calculus questions; grade labs}
		\resitem{8 to 15 hours per week}
	\end{itemize}
	}
\end{comment}
\end{itemize}
%---------END WORK EXPERIENCE--------%

%---------BEGIN CERTS------------%
\resheading{Professional Certifications}
\begin{itemize}
    \item
       \ressubheading{\href{https://ctme.caltech.edu/programs-for-individuals/software-engineering-open/devops-pgp}{Caltech DevOps Post Graduate Program Certificate}
       }{\href{https://ctme.caltech.edu/}{Caltech CTME}
       }{cloud-native development and agile operations
       }{Ongoing (Nov 2020 - May 2021)}
    \item
        \ressubheading{\href{https://www.isc2.org/Certifications/CSSLP}{CSSLP (Member ID: 788005)}
        }{\href{https://www.isc2.org/}{$(ISC)^2$}
        }{secure software throughout development lifecycle
        }{Oct 2020 -- Sep 2023}
     \item
        \ressubheading{\href{https://ctme.caltech.edu/programs-for-individuals/advanced-engineering-open/model-based-systems-engineering-certificate-open}{Model-Based Systems Engineering}
        }{\href{https://ctme.caltech.edu/}{Caltech CTME}
        }{SysML training and model creation
        }{2019}
      \item
        \ressubheading{\href{https://ctme.caltech.edu/programs-for-individuals/advanced-engineering-open/systems-engineering-fundamentals-open}{System Engineering Fundamentals}
        }{\href{https://ctme.caltech.edu/}{Caltech CTME}
        }{Practical methods and tools for system engineering
        }{2019}
    \item
        \ressubheading{\href{https://certification.comptia.org/certifications/security}{Security+}
        }{\href{https://certification.comptia.org/home}{CompTIA}
        }{Application, network, and device security
        }{Feb 2018 -- Feb 2021}
\end{itemize}
~
%---------END CERTS------------%

%-----------EDUCATION-----------------%
\resheading{Education}
	\begin{itemize}
%  \item
%			\ressubheading{\href{www.umn.edu}{University of Minnesota - Twin Cities}}{Minneapolis, MN}{Ph.D. Scientific Computation; GPA: 4.00 \, \, (no longer pursuing)}{Aug 2014 -- Mar 2015}
%			{ \footnotesize
%			\begin{itemize}
%					\resitem{Advisor: Dr. Yousef Saad} 
%				\end{itemize}
%				}
		\item
			\ressubheading{\href{www.mtu.edu}{Michigan Technological University}}{Houghton, MI}{M.S. in Applied Mathematics; GPA: 4.00}{Aug 2012 -- June 2014}
                                           \begin{comment}
				{ \footnotesize
				\begin{itemize}
					\resitem{Advisor: Dr. Jiguang Sun} 
				\end{itemize}
				}
                                          \end{comment}
		\item
			\ressubheading{\href{www.mtu.edu}{Michigan Technological University}}{Houghton, MI}{B.S. in Physics and Applied/Computational Mathematics; GPA:3.94}{Aug 2008 -- Apr 2012}
                                           \begin{comment}
				{ \footnotesize
				\begin{itemize}
					\resitem{Graduated Summa Cum Laude} 
				\end{itemize}
				}
                                          \end{comment}
\begin{comment}%high school eduation. Not included
		\item
			\ressubheading{\href{http://www.isd12.org/chs/}{Centennial High School}}{Circle Pines, MN}{GPA:3.79}{Sep. 2003 - June 2008}
                                           \begin{comment}
				{ \footnotesize
				\begin{itemize}
				\resitem{Graduated with honors}
				\end{itemize}
				}
\end{comment}
	\end{itemize} % End Education list

%---------END EDUCATION------------%

%---------BEGIN SKILLS-----------%
\resheading{Skills}
\begin{itemize}
  \resitem{\textbf{Practices:} Agile methodologies, multi-language development, DevSecOps, Software Modeling}
  \resitem{\textbf{Tools:} Fortify, GitHub, git, Jenkins, JIRA,  \LaTeX, Linux, Make, \textsc{matlab}, Maven, SharePoint}
  \resitem{\textbf{Languages:} BASH, C, C++, Fortran (Modern and 77), Java, JavaScript, Python, SysML, SQL}
\end{itemize}
%----------END SKILLS-----------%

%\newpage
%---------BEGIN ACHIEVEMENTS---------%
\resheading{Achievements}
\begin{itemize}
\item
\ressubheading{NG IP trade secret awards}{MS IP Committee}{3 related to space and weather effects on communications}{2018-2019}
\item
\ressubheading{Outstanding Teaching Award}{Michigan Tech Dept. of Mathematics}{Graduate Level}{2014}
\item
\ressubheading{Co-Recipient of \href{http://www.mtu.edu/physics/department/profile/awards/shepherd.html}{Ian W. Shepherd award}}{Michigan Tech Dept. of Physics}{"presented each year to the most outstanding physics graduate(s)"}{2012}
\begin{comment}
\item
\ressubheading{Departmental Scholar}{Michigan Tech Dept. of Physics}{}{2011}
\item
\ressubheading{Certificate of Merit}{Dept. of Mathematical Sciences}{For my performance in the Applied Vector/Tensor Analysis course}{Dec. 2011}
\end{comment}
\end{itemize}
%---------END ACHIEVEMENTS-----------%
\end{document}

%---------BEGIN RESEARCH EXPERIENCE--------%
\resheading{Research Experience}
\begin{itemize}
\item%Senior research
	\ressubheading{Senior Research (BS degree)}{Houghton, MI}{Computational analysis of spectra arising from Mo doped Tungstenite}{2011 - 2012}
	{\footnotesize
	\begin{itemize}
		\resitem{Advisor: Dr. John Jaszczak}
%		\resitem{Compared to experimentally obtained spectra}
	\end{itemize}
	}
\item%LPSA
	\ressubheading{Lunar and Planetary Space Academy}{NASA - Goddard, MD}{Instrumentation development for space based Gamma Ray Spectroscopy}{Summer 2011}
	{\footnotesize
	\begin{itemize}
		\resitem{Mentor: Dr. Ann Parsons}
%		\resitem{Developed calibration code for an active shielding detector}
%		\resitem{Worked on characterization of Neutron Source}	
%		\resitem{Participated in field studies of basalt formations in the scablands in Washington State}	
	\end{itemize}
	}
\item%Dr. Yap's Lab
	\ressubheading{Yap Research Group}{Michigan Tech}{Boron Nitride Nanotube (BNNT) synthesis and application}{Summer 2010}
%	{\footnotesize
%	\begin{itemize}
%	%	\resitem{Graduate Student lead researcher: Chee Huei Lee}
%	%	\resitem{Development of techniques to synthesize carbon-doped BNNTs}
%%		\resitem{Development of solid state radiation detector based upon BNNT substrate}
%		\resitem{Funding provided by Michigan Space Grant Consortium}
%	\end{itemize}
%	}
\end{itemize}
%---------END RESEARCH EXPERIENCE--------%

\end{document}
%---------BEGIN EXTRA CURRICULARS---------%
\resheading{Extra Curricular Activities}
\begin{itemize}
\item
	\ressubheading{Broomball}{}{Player (2009 - 2015) and Team Captain (2011-2014)}{}
\item
  \ressubheading{SPS Member}{}{Public outreach explaining physics concepts to elementary students}{}
\end{itemize}
%---------END EXTRA CURRICULARS-----------%






%Only Print References If Requested!  Maybe even put it in it's own page.  Must have same heading as first page.
%%%%%%%%%%%%%%%%%%%%%%
\newpage
\myheader
\resheading{References}
	\begin{center}
		\begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}  l l l }
			
		\end{tabular*}
	\end{center}
	
%\end{document}


% ADDITIONAL WORK EXPERIENCE NOT INCLUDED	OR OLD

\item%Burger King
	\ressubheading{Burger King}{Forest Lake, MN}{Crew Member}{Apr 2006 -- Aug 2008\\June 2009 -- Aug 2009}
	{\footnotesize
	\begin{itemize}
		\resitem{Supervisors: Chad Herbert, Colette Vincent}
	\end{itemize}
	}	


%%%%%%%%%%%%%%%%%%%%%%%%
% GENERAL RESUME NOTES %
%%%%%%%%%%%%%%%%%%%%%%%%
Need to brush up on the skills section?  Here are some really good ideas:

- Communication: The ability to express and interpret ideas and convey knowledge. 
Skills like speaking effectively, writing concisely, listening attentively, expressing ideas, 
reporting information, editing, interviewing, and facilitating group discussion. 
 
- Research and Planning: The ability to search for specific knowledge and formulate a 
program for a definite course of action. Skills like forecasting, predicting, identifying 
issues, finding alternatives, gathering information, solving problems, setting goals, 
extracting information, and developing strategies. 
 
- Human Relations: The ability to apply interpersonal skills to resolve conflict, relate to 
people, and help people. Skills like providing support for others, listening, delegating 
with respect, representing others, asserting, developing rapport, and perceiving 
feelings. 
 
- Management, Organization, Leadership: The ability to supervise others and guide 
individuals and groups towards the completion of tasks. Skills like managing groups, 
selling ideas, making decisions, managing conflict, coordinating tasks, teaching, 
enlisting help. 

Source: 
http://www.squawkfox.com/2009/03/08/6-action-words-that-make-your-resume-rock/

Other Resources: 
http://www.tvmier.com/Resume_Education.html

